---
title: "Article 3 - Farmer study provides water use lessons"
description: |
  A short description of the post.
author:
  - name: Louise Lilin
    url: {}
date: 12-14-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## I - SOURCE OF THE ARTICLE WITH PUBLICATION DATE AND WORD COUNT:

Source of the article: https://www.nzherald.co.nz/the-country/news/farmer-study-provides-water-use-lessons/SWT3UKV3FVERGXZAIW2EWPUFWY/

Word count : 419

## II - VOCABULARY

| Word from the text  | Synonym/ definition  |
|---|---|
| Groundwater  | Underground water resources (= nappes phréatiques)  |
| Over-allocation  | More resources have been promised/ allocated than the existing quantity  |
| To gauge  | To measure  |
| Surface water  | Opposed to ground water : water on the earth surface, such as rivers, lakes and wetlands  |
| Cash crops  |Crops grown to sell for profit (and not for subsistence of the farmer’s family), often holding some export value|
| Soft data  |Informations about things that are difficult to measure|
| Catchment scale  |Area of land where precipitation collects and drains off into a common outlet|

## III - ANALYSIS TABLE ABOUT THE STUDY

| Researchers  | Ho Chi Minh University 
Flinders University 
H.M. Vu, M. Shanafield, T.T. Nhat, D. Partington, O. Batelaan  |
|---|---|
| Published in ? when  |Journal of Hydrology : Regional Studies, August 2020|
| General topic  |Mapping of groundwater in the La Vi River Basin in Vietnam|
| Procedure/ what was examined  |Interview of vietnamese farmers (= soft data)(to estimate their use of land and water)
Modellisation of the spatial distribution of groundwater |
| Conclusions/ discovery  |Elementary informations on the groundwater distribution, usable to improve water management during water scarcity in the basin
A simple and cost-effective method functional in other agricultural regions lacking data on water|
| Reamining questions  |/|

## IV - Article : Farmer study provides water use lessons

Research into Vietnamese farmers' *groundwater* usage could have benefits for their Australian counterparts, according to a study from Flinders University.

The heavily agricultural La Vi River Basin in Vietnam was the focus of the study, forming part of a five-year project funded by the Australian Centre for International Agricultural Research (ACIAR).

"Groundwater use for food and industrial production is increasing globally, putting pressure on groundwater resources and associated ecosystems," said Flinders University Professor Okke Batelaan.

"In many countries, particularly in developing regions as well as Australia's Murray-Darling Basin (MDB), this abstraction may be poorly organised and not regularly *gauged* for data."

*Over-allocation* of *surface water* for growing food crops is shifting agriculture and other industry to use groundwater - which was much more difficult to measure and monitor.

Using local farmer knowledge as "*soft data*" to estimate groundwater use in modelling was a helpful tool in mapping sustainable use of scarce resources, Flinders University experts said.

Environmental and water researchers from Flinders have described the technique in a new paper published online in the Journal of Hydrology: Regional Studies.

The researchers, including John Allwright fellow Flinders PhD candidate Manh Hai Vu, interviewed local farmers about their land use, agricultural practices and water use.

The approach was very helpful in collecting base line information for future use – particularly when climate change or variable rainfall posed a threat to future water management, said Dr Margaret Shanafield, from the National Centre for Groundwater Research and Training based at Flinders University.

"Although often thought of as a wet, tropical climate, Vietnam's South central coast has long dry seasons, and hence suffers from surface water shortages, similar to many parts of Australia," said Shanafield.

"Groundwater use provides a significant solution to local farmers for producing *cash crops* and improving livelihood."

The system could also be used in Australia in areas such as the northern part of the MDB where groundwater is largely unmonitored.

The study developed a cost-effective and computationally simple solutions for estimating groundwater abstraction in data-poor agricultural regions, researchers said.

- Mapping *catchment-scale*unmonitored groundwater abstractions: Approaches based on soft data (2020) by Vu MH Vu, M Shanafield, TT Nhat, D Partington, O Batelaan has been published in the Journal of Hydrology: Regional Studies


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

{% if page.comments %}
<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = https://llilin.github.io/llilin_blog/posts/2020-12-14-article-3-farmer-study-provides-water-use-lessons/ ;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = article3; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://llilin.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
{% endif %}
